---
title: "Resample Matrix"
author: "SWC"
date: "02/02/2015"
output: html_document
---

# Introduction
Suppose I have a legacy data file that consists of 1's and 0's, like this:

00000000

00001100

00011110

00111110

00010110

00001000

(except it's much larger - probably 80x80).  I want to convert it to a black-and-white image, using a 4x4 patch of white pixels for each 0 and an equivalent patch of black pixels for each 1.  How can we do that in R?

# Code
Load the functions needed for this:
```{r}
#load the source files
source('readMatrix.R')
source('resampleMatrix.R')
source('plotMatrix.R')
```

Load the example data
```{r}
exampleFile<-'data/example.dat'
dat <- readMatrix(exampleFile)
```

## Original data
```{r, echo=FALSE}
plotMatrix(dat)
```
The example data is `r nrow(dat)` rows by `r ncol(dat)`.
The output will be 4 times larger in both dimensions


```{r}
newSize<-4
newMat<-resampleMatrix(dat,newSize)
```

## New data
```{r, echo=FALSE}
plotMatrix(newMat)
```

# Exporting images
It's easy to export out new matrix in a format suitable for insertion into another document

```{r}
require(png) #load the package for dealing with .png files

writePNG(dat,
         target='output/oldimage.png')
writePNG(newMat,
         target='output/newimage.png')
```